Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb

### 2018-04-18 nb_px_paper/cover_letter.tex
Updated paper title for journal submission. Submitted this commit to NIM-B.

\begin{letter}{Editorial Board \\
Nuclear Instruments and Methods in Physics Research Section B: \\
Beam Interactions with Materials and Atoms}

@@

\noindent I am writing to submit an original manuscript entitled \enquote{\emph{Measurement of nuclear excitation functions for proton induced reactions (E$_{\text{p}}$ = 40--90 MeV) on natural Nb}}  for publication in Nuclear Instruments and Methods in Physics Research Section B.  This manuscript describes an original work conducted by myself, the first and corresponding author, along with my co-authors and collaborators Lee A. Bernstein\footnotemark[1]\footnotemark[2], Eva R. Birnbaum\footnotemark[3], Jonathan W. Engle\footnotemark[4], Stephen A. Graves\footnotemark[5], Toshihiko Kawano\footnotemark[6], Amanda M. Lewis\footnotemark[2], and Francois M. Nortier\footnotemark[3].

@@

If I may make one personal request, it would mean a great deal to me if the processing of this manuscript can be expedited in any way, to be able to get it to the referees as quickly as possible without any loss of integrity to the review process. 
I am in my last several months of my PhD studies, and if this manuscript is able to be accepted by 10 June 2018, I will be able to include it as part of my doctoral dissertation.
Along with many rounds of revisions with my co-authors, we have put great effort into producing what we consider a manuscript of significant merit to the field, which provides an example of rigorous analysis and uncertainty quantification for cross section data with wide-ranging applications.  
I believe that this review process should hopefully be quite smooth, but anything that can be done to help start it as rapidly as possible would be invaluable in allowing me to make this deadline.

>>>>

\begin{letter}{Dr. Mark Breese, or the Editorial Board \\
Nuclear Instruments and Methods in Physics Research Section B: \\
Beam Interactions with Materials and Atoms}

@@

\noindent I am writing to submit an original manuscript entitled \enquote{\emph{Excitation functions for (p,x) reactions of niobium (E$_{\text{p}}$ = 40--90 MeV):  development of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as an intermediate-energy proton monitor}}  for publication in Nuclear Instruments and Methods in Physics Research Section B.  This manuscript describes an original work conducted by myself, the first and corresponding author, along with my co-authors and collaborators Lee A. Bernstein\footnotemark[1]\footnotemark[2], Eva R. Birnbaum\footnotemark[3], Jonathan W. Engle\footnotemark[4], Stephen A. Graves\footnotemark[5], Toshihiko Kawano\footnotemark[6], Amanda M. Lewis\footnotemark[2], and Francois M. Nortier\footnotemark[3].

@@

If I may make one personal request, it would mean a great deal to me if the processing of this manuscript can be expedited in any way, to be able to get it to the referees as quickly as possible without any loss of integrity to the review process. 
I am in my last several months of my PhD studies, and if this manuscript is able to be accepted for the July 2018 issue of NIM B, I will be able to include it as part of my doctoral dissertation.
Along with many rounds of revisions with my co-authors, we have put great effort into producing what we consider a manuscript of significant merit to the field, which provides an example of rigorous analysis and uncertainty quantification for cross section data with wide-ranging applications.  
I believe that this review process should hopefully be quite smooth, but anything that can be done to help start it as rapidly as possible would be invaluable in allowing me to make this deadline.
